---
title: "Bibliometrix analysis using journals"
output: html_notebook
---
### Contents{#con}
1. [Search string](#ss)
2. [General](#gen)
3. [Lotka’s Law coefficient estimation](#lotka)
4. [Network matricies](#nm)
5. [Bibliographic coupling](#bc)
6. [Co-Word Analysis](#cw)
7. [Historical Direct Citation Network](#hdcn)


### Search string{#ss}

>  TITLE ( "dynamic capability" )  AND  SUBJAREA ( arts  OR  busi  OR  deci  OR  econ  OR  psyc  OR  soci )

  
***  
#### Plugin the library
```{r Plugin the library}
library(bibliometrix)
```

***  
Load file (or several) \\ - use double slash or normal slash - /  
```{r}
myfile <- 'C:\\Users\\TL66LU\\Nextcloud\\GitHub\\aiprobono\\bibliometrix\\scopus_dynamic_capability.bib'
```
***  

Convert to r understandable structure
```{r}
bib_df<-convert2df(file = myfile, dbsource = "scopus", format = "bibtex")
```
  
***  

Analyze the data
```{r}
myresults <- biblioAnalysis(bib_df, sep = ";")
```
***      
### General{#gen}
[Contents](#con)  
Summarize 10 results
```{r}
sor<-summary(myresults,10,FALSE)
```
Don't know where it takes countries from. It parses it from some field.

Plot 10 results
```{r}
plot(x=myresults,k=10,pause=FALSE)
```
Analyze citations and get 10 most cited articles
```{r}
CR<-citations(bib_df, field = "article", sep = ";")
cbind(CR$Cited[1:10])
```

Analyze citations and get 10 most cited authors
```{r}
CR <- citations(bib_df, field = "author", sep = ";")
cbind(CR$Cited[1:10])
```


Local citations:
```{r}
CR <- localCitations(bib_df, sep = ";")
CR$Authors[1:10,]
CR$Papers[1:10,]
```

Dominance ranking
```{r}
DF <- dominance(myresults, k = 10)
DF
```

H-index
```{r}
authors=gsub(","," ",names(myresults$Authors)[1:10])
indices <- Hindex(bib_df, field = "author", elements=authors, sep = ";", years = 50)
indices$H
```
### Lotka’s Law coefficient estimation{#lotka}
[Contents](#con)  

```{r}
L <- lotka(myresults)
# Author Productivity. Empirical Distribution
L$AuthorProd
# Beta
L$Beta
# Constatnt
L$C
# Goodness of fit
L$R2
# P-value of K-S two sample test
L$p.value
```
```{r}
# Observed distribution
Observed=L$AuthorProd[,3]

# Theoretical distribution with Beta = 2
Theoretical=10^(log10(L$C)-2*log10(L$AuthorProd[,1]))

plot(L$AuthorProd[,1],Theoretical,type="l",col="red",ylim=c(0, 1), xlab="Articles",ylab="Freq. of Authors",main="Scientific Productivity")
lines(L$AuthorProd[,1],Observed,col="blue")
legend(x="topright",c("Theoretical (B=2)","Observed"),col=c("red","blue"),lty = c(1,1,1),cex=0.6,bty="n")
```
Don't know how to comment upon these results. Does this mean authors are being not that productive?

### Network matricies{#nm}
[Contents](#con)  

#### Biparite networks

```{r}
A <- cocMatrix(bib_df, Field = "SO", sep = ";")
sort(Matrix::colSums(A), decreasing = TRUE)[1:5]
```
#### Citation network
```{r}
A <- cocMatrix(bib_df, Field = "CR", sep = ".  ")
sort(Matrix::colSums(A), decreasing = TRUE)[1:5]
```
Did not understand how to interpret it.

#### Author network

```{r}
 A <- cocMatrix(bib_df, Field = "AU", sep = ";")
sort(Matrix::colSums(A), decreasing = TRUE)[1:5]
```

#### Country network
```{r}
AuCo <- metaTagExtraction(bib_df, Field = "AU_CO", sep = ";")
A <- cocMatrix(AuCo, Field = "AU_CO", sep = ";")
sort(Matrix::colSums(A), decreasing = TRUE)[1:10]
```
#### Author keyword nw

```{r}
A <- cocMatrix(bib_df, Field = "DE", sep = ";")
sort(Matrix::colSums(A), decreasing = TRUE)[1:10]
```
#### Keyword nw

```{r}
A <- cocMatrix(bib_df, Field = "ID", sep = ";")
sort(Matrix::colSums(A), decreasing = TRUE)[1:30]
```
#### Page count nw

```{r eval=FALSE, include=FALSE}
A <- cocMatrix(bib_df, Field = "PG", sep = ";")
sort(Matrix::colSums(A), decreasing = TRUE)[1:30]
```
Doesn't work as the dataset has no such a field.

### Bibliographic coupling{#bc}
[Contents](#con)  

```{r}
NetMatrix <- biblioNetwork(bib_df, analysis = "coupling", network = "authors", sep = ";")


net=networkPlot(NetMatrix,  normalize = "salton", weighted=NULL, n = 20, Title = "Authors' Coupling", type = "fruchterman", size=5,size.cex=T,remove.multiple=TRUE,labelsize=0.8,label.n=20,label.cex=F)
```
#### Collaborating authors

```{r}
NetMatrix <- biblioNetwork(bib_df, analysis = "collaboration", network = "authors", sep = ";")
net=networkPlot(NetMatrix,  normalize = "salton", weighted=NULL, n = 100, Title = "Authors' Coupling", type = "fruchterman", size=5,size.cex=T,remove.multiple=TRUE,labelsize=0.5,label.n=10,label.cex=F)
```
#### Co-citation

```{r}
NetMatrix <- biblioNetwork(bib_df, analysis = "co-citation", network = "references", sep = ".  ")
net=networkPlot(NetMatrix,  normalize = "salton", weighted=NULL, n = 50, Title = "Co-citation", type = "fruchterman", size=5,size.cex=T,remove.multiple=TRUE,labelsize=0.3,label.n=10,label.cex=F)
```
#### Co-citation network
```{r}
NetMatrix <- biblioNetwork(bib_df, analysis = "co-citation", network = "references", sep = ";")

# Plot the network
net=networkPlot(NetMatrix, n = 30, Title = "Co-Citation Network", type = "fruchterman", size=T, remove.multiple=FALSE, labelsize=0.7,edgesize = 5)
```

#### Keyword co-occurrences
```{r}
NetMatrix <- biblioNetwork(bib_df, analysis = "co-occurrences", network = "keywords", sep = ";")

# Plot the network
net=networkPlot(NetMatrix, normalize="association", weighted=T, n = 30, Title = "Keyword Co-occurrences", type = "fruchterman", size=T,edgesize = 5,labelsize=0.7)
```
### Co-Word Analysis: The conceptual structure of a field{#cw}
[Contents](#con)  

```{r}
png(pointsize=10, width=2800, height=2000, res=600)
par(mar=c(5, 4, 4, 2))
CS <- conceptualStructure(bib_df,field="ID", method="CA", minDegree=4, clust=5, stemming=FALSE, labelsize=6, documents=10)
```


### Historical Direct Citation Network{#hdcn}
```{r}
options(width=130)
histResults <- histNetwork(bib_df, min.citations = 1, sep = ";")

```
```{r}
net <- histPlot(histResults, n=15, size = 10, labelsize=5)
```
Doesn't work due to some error.
The end.